%-------------------------
% Sam Bock Resume
% Author : Sam Bock
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeCampusInvolvement}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}, #2 & #3 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{center}
  \textbf{\Huge \ \scshape Sam Bock} \\ \vspace{3pt}
   \href{mailto:sabock@calpoly.edu}{sabock@calpoly.edu} $|$ \small 909-609-9291 $|$ \href{https://www.sambock.dev}{sambock.dev} $|$ \href{https://www.linkedin.com/in/smbock42}{linkedin.com/in/smbock42} $|$ \href{https://www.github.com/smbock42}{github.com/smbock42}

\end{center}

%-----------SUMMARY-----------------
\section{Summary}
\small{Software engineer with hands-on experience in full-stack development, AI/ML research, and cybersecurity automation. Passionate about building scalable applications, optimizing workflows, and solving real-world problems with cutting-edge technology. Proficient in cloud platforms, security automation, and database-driven applications, with a track record of delivering impactful results.}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University, San Luis Obispo}{San Luis Obispo, CA}
      {Bachelor of Science in Computer Science;  GPA: 3.7}{Sept. 2021 -- June. 2025}\\[3mm]
      \textbf{Relevant Coursework:} Deep Learning, Distributed Computing, Database Systems, Data Science, Algorithms, Computer Security, Software Engineering, Systems Programming, Operating Systems, Programming Languages, \\Mobile App Development
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{Sunnyvale, CA}
      {Lockheed Martin Space}{June 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Full Stack Development}
          {Developed a web application for managing project reviews, enabling stakeholders to create, assign, and track reviews in real-time.}
        \resumeItem{Project Management}
          {Managed end-to-end project lifecycle, including approvals process and setting up development environments.}
        \resumeItem{Technologies Used}
          {Next.js, TypeScript, Prisma, Supabase, Tailwind CSS}
      \resumeItemListEnd

      \resumeSubheading
      {AI/ML Research Intern}{Sunnyvale, CA}
      {Lockheed Martin Space}{June 2023 -- Oct 2023}
      \resumeItemListStart
        \resumeItem{Object Detection and Computer Vision}
          {Developed models for detecting anomalies in satellite data.}
        \resumeItem{Model Optimization}
          {Enhanced model performance by fine-tuning parameters and implementing data augmentation strategies.}
        \resumeItem{Technologies Used}
          {Python, TensorFlow, Keras, OpenCV, Jupyter Notebooks}
      \resumeItemListEnd

      \resumeSubheading
      {IT Engineering Intern}{San Luis Obispo, CA}
      {HaptX Inc.}{Mar 2023 -- June 2023}
      \resumeItemListStart
        \resumeItem{Conditional Access Policies}
          {Hardened existing conditional access policies to enhance security based on user risk factors.}
        \resumeItem{Hardware Management}{Repaired, upgraded, and optimized company workspaces and hardware.}
        \resumeItem{Technologies Used}
          {Microsoft Azure, Microsoft Intune}
        
      \resumeItemListEnd

    \resumeSubheading
      {Junior Security Operations Center Analyst}{San Luis Obispo, CA}
      {Cal Poly Information Technology Services}{June 2022 -- Feb 2023}
      \resumeItemListStart
        \resumeItem{Security Incident Response}
          {Analyze and take action against suspicious logins, phishing emails, and network traffic using Splunk, Microsoft Azure, and other security tools.}
        \resumeItem{Analyst Action Automator}
          {Developed a tool to automate incident response tasks, reducing total execution time by 80\%}
        \resumeItem{Technologies Used}{Splunk, Python, Slack API, Linux, Splunk Soar Playgrounds}
       
        
      \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Plan2Gather}{Developed web app that allows users to create events and analyzes best times to meet based on a group of inputs. Built using Vite, Nx, Cloudflare KV. \href{https://plan2gather.net}{Website: plan2gather.net} }
    \resumeSubItem{Portfolio Website}{Built a portfolio website using Next.js, TypeScript, and Tailwind CSS. \href{https://sambock.dev}{Website: sambock.dev}}
    \resumeSubItem{HomeLab}{Configured a home server using Cloudflare Zero Trust hosting a suite of applications.}
    \resumeSubItem{Custom PC Builder and Trader}{Developed a web app using PostgreSQL and Python fastAPI for building and trading PCs and PC parts. \href{https://github.com/AdamDelRio/Custom-PC-Builder-and-Trader}{Github: https://github.com/AdamDelRio/Custom-PC-Builder-and-Trader}}

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}

\textbf{Languages:} Python, SQL, TypeScript, Tailwind CSS, Java, C, C++\\
\textbf{Skills:} Git, Linux, Next.js, React.js, Node.js, Microsoft Azure, Docker, Supabase, Jira, Splunk,\\ Testing and Debugging, Agile Development, Scrum Methodology

%-------------------------------------------
\end{document}
